---
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}
library(readr)
library(tidyverse)
#top 50 liberal arts colleges
Top_50_Liberal_Arts_Colleges_2015_2018_College <- read_csv("~/Library/Mobile Documents/com~apple~CloudDocs/Downloads/Top 50 Liberal Arts Colleges 2015-2018 - College.csv")

#yield data for all colleges
Yeild_2022_data_Sheet_1_drvadm2022 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/Yeild_2022_data - Sheet 1 - drvadm2022.csv")

Divest_data_2022 <- left_join

#pulling out yeild 2022 Yield data for top 50 liberal arts colleges
Lib_arts_yield_2022 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,Yeild_2022_data_Sheet_1_drvadm2022)


Yield_data_2021 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/Yield_data - 2021.csv")
View(Yield_data_2021)

#pulling out  2021 Yield data for top 50 liberal arts colleges
Lib_arts_yield_2021 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,Yield_data_2021)

Yield_data_2020 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/Yield_data - 2020.csv")


#pulling out 2020 Yield data for top 50 liberal arts colleges
Lib_arts_yield_2020 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,Yield_data_2020)

Lib_arts_yield_2020 <-
  Lib_arts_yield_2020|>
  mutate(admit_percent = ADMSSN/APPLCN*100,
         yield_rate = ENRLT/ADMSSN*100)

Yield_data_2019 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/Yield_data - 2019.csv")

#pulling out 2019 Yield data for top 50 liberal arts colleges
Lib_arts_yield_2019 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,Yield_data_2019)

Lib_arts_yield_2019<-
  Lib_arts_yield_2019|>
  mutate(admit_percent = ADMSSN/APPLCN*100,
         yield_rate = ENRLT/ADMSSN*100)

Yield_data_2018 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/Yield_data - 2018.csv")
#pulling out 2018 Yield data for top 50 liberal arts colleges
Lib_arts_yield_2018 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,Yield_data_2018)

Lib_arts_yield_2018 <-
  Lib_arts_yield_2018|>
  mutate(admit_percent = ADMSSN/APPLCN*100,
         yield_rate = ENRLT/ADMSSN*100)

Yield_data_2017 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/Yield_data - 2017 (1).csv")

#pulling out 2017 Yield data for top 50 liberal arts colleges
Lib_arts_yield_2017 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,Yield_data_2017)

Lib_arts_yield_2017 <-
  Lib_arts_yield_2017|>
  mutate(admit_percent = ADMSSN/APPLCN*100,
         yield_rate = ENRLT/ADMSSN*100)
#2016
Yield_data_2016 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/Yield_data - 2016.csv")


#pulling out 2016 Yield data for top 50 liberal arts colleges
Lib_arts_yield_2016 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,Yield_data_2016)

Lib_arts_yield_2016 <-
  Lib_arts_yield_2016|>
  mutate(admit_percent = ADMSSN/APPLCN*100,
         yield_rate = ENRLT/ADMSSN*100)


Yield_data_2015 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/Yield_data - 2015.csv")

Lib_arts_yield_2015 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,Yield_data_2015)

Lib_arts_yield_2015 <-
  Lib_arts_yield_2015|>
  mutate(admit_percent = ADMSSN/APPLCN*100,
         yield_rate = ENRLT/ADMSSN*100)

Yield_data_2014 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/Yield_data - 2014 (3).csv")


Lib_arts_yield_2014 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,Yield_data_2014)

Lib_arts_yield_2014 <-
  Lib_arts_yield_2014|>
  mutate(admit_percent = ADMSSN/APPLCN*100,
         yield_rate = ENRLT/ADMSSN*100)


#2013
Yield_data_2013 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/Yield_data - 2013 (1).csv")

Lib_arts_yield_2013<-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,Yield_data_2013) 

Lib_arts_yield_2013 <-
  Lib_arts_yield_2013|>
  mutate(ENRLT = as.double(ENRLT),
         APPLCN = as.double(APPLCN),
         ADMSSN = as.double(ADMSSN),
         admit_percent = ADMSSN/APPLCN*100,
         yield_rate = ENRLT/ADMSSN*100
         )
#2012
Yield_data_2012 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/Yield_data - 2012 (1).csv")

Lib_arts_yield_2012<-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,Yield_data_2012) 

Lib_arts_yield_2012<-
  Lib_arts_yield_2012|>
  mutate(ENRLT = as.double(ENRLT),
         APPLCN = as.double(APPLCN),
         ADMSSN = as.double(ADMSSN),
         admit_percent = ADMSSN/APPLCN*100,
         yield_rate = ENRLT/ADMSSN*100
         )
#2011
Yield_data_2011 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/Yield_data - 2011.csv")

Lib_arts_yield_2011<-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,Yield_data_2011) 

Lib_arts_yield_2011<-
  Lib_arts_yield_2011|>
  mutate(ENRLT = as.double(ENRLT),
         APPLCN = as.double(APPLCN),
         ADMSSN = as.double(ADMSSN),
         admit_percent = ADMSSN/APPLCN*100,
         yield_rate = ENRLT/ADMSSN*100
         )
#2010
Yield_data_2010 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/Top 50 Liberal Arts Colleges 2015-2018 - 2010.csv")

Lib_arts_yield_2010 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,Yield_data_2010) 

Lib_arts_yield_2010<-
  Lib_arts_yield_2010|>
  mutate(ENRLT = as.double(ENRLT),
         APPLCN = as.double(APPLCN),
         ADMSSN = as.double(ADMSSN),
         admit_percent = ADMSSN/APPLCN*100,
         yield_rate = ENRLT/ADMSSN*100
         )
#2009
Yield_data_2009 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/Yield_data - 2009.csv")

Lib_arts_yield_2009 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,Yield_data_2009) 

Lib_arts_yield_2009<-
  Lib_arts_yield_2009|>
  mutate(ENRLT = as.double(ENRLT),
         APPLCN = as.double(APPLCN),
         ADMSSN = as.double(ADMSSN),
         admit_percent = ADMSSN/APPLCN*100,
         yield_rate = ENRLT/ADMSSN*100
         )
#2008

Yield_data_2008 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/Yield_data - 2008 (1).csv")

Lib_arts_yield_2008 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,Yield_data_2008) 

Lib_arts_yield_2008<-
  Lib_arts_yield_2008|>
  mutate(ENRLT = as.double(ENRLT),
         APPLCN = as.double(APPLCN),
         ADMSSN = as.double(ADMSSN),
         admit_percent = ADMSSN/APPLCN*100,
         yield_rate = ENRLT/ADMSSN*100
         )

#2007

Yield_data_2007 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/Yield_data - 2007.csv")

Lib_arts_yield_2007 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,Yield_data_2007) 

Lib_arts_yield_2007<-
  Lib_arts_yield_2007|>
  mutate(ENRLT = as.double(ENRLT),
         APPLCN = as.double(APPLCN),
         ADMSSN = as.double(ADMSSN),
         admit_percent = ADMSSN/APPLCN*100,
         yield_rate = ENRLT/ADMSSN*100
         )

#2006

Yield_data_2006 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/Yield_data - 2006.csv")

Lib_arts_yield_2006 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,Yield_data_2006) 

Lib_arts_yield_2006<-
Lib_arts_yield_2006|>
  mutate(ENRLT = as.double(ENRLT),
         APPLCN = as.double(APPLCN),
         ADMSSN = as.double(ADMSSN),
         admit_percent = ADMSSN/APPLCN*100,
         yield_rate = ENRLT/ADMSSN*100
         )

write_csv(Lib_arts_yield_2006, "Lib_arts_yield_2006.csv")
write_csv(Lib_arts_yield_2007, "Lib_arts_yield_2007.csv")
write_csv(Lib_arts_yield_2008, "Lib_arts_yield_2008.csv")
write_csv(Lib_arts_yield_2009, "Lib_arts_yield_2009.csv")
write_csv(Lib_arts_yield_2010, "Lib_arts_yield_2010.csv")
write_csv(Lib_arts_yield_2011, "Lib_arts_yield_2011.csv")
write_csv(Lib_arts_yield_2012, "Lib_arts_yield_2012.csv")
write_csv(Lib_arts_yield_2013, "Lib_arts_yield_2013.csv")
write_csv(Lib_arts_yield_2014, "Lib_arts_yield_2014.csv")
write_csv(Lib_arts_yield_2015, "Lib_arts_yield_2015.csv")
write_csv(Lib_arts_yield_2016, "Lib_arts_yield_2016.csv")
write_csv(Lib_arts_yield_2017, "Lib_arts_yield_2017.csv")
write_csv(Lib_arts_yield_2018, "Lib_arts_yield_2018.csv")
write_csv(Lib_arts_yield_2019, "Lib_arts_yield_2019.csv")
write_csv(Lib_arts_yield_2020, "Lib_arts_yield_2020.csv")
write_csv(Lib_arts_yield_2021, "Lib_arts_yield_2021.csv")
write_csv(Lib_arts_yield_2022, "Lib_arts_yield_2022.csv")

```


```{r}
#tuition 2022

tuition_data_2022 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/tuition_data - 2022.csv")

Lib_arts_tuition_2022 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,tuition_data_2022) 

#2021
tuition_data_2021 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/tuition_data - 2021.csv")

Lib_arts_tuition_2021 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,tuition_data_2021) 

#2020

tuition_data_2020 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/tuition_data - 2020.csv")

Lib_arts_tuition_2020 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,tuition_data_2020) 

#2019

tuition_data_2019 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/tuition_data - 2019.csv")

Lib_arts_tuition_2019 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,tuition_data_2019)

#2018

tuition_data_2018 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/tuition_data - 2018.csv")

Lib_arts_tuition_2018 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,tuition_data_2018)

#2017
tuition_data_2017 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/tuition_data - 2017.csv")


Lib_arts_tuition_2017 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,tuition_data_2017)

#2016

tuition_data_2016 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/tuition_data - 2016.csv")

Lib_arts_tuition_2016 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,tuition_data_2016)

#2015

tuition_data_2015 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/tuition_data - 2015.csv")

Lib_arts_tuition_2015 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,tuition_data_2015)

#2014

tuition_data_2014 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/tuition_data - 2014.csv")

Lib_arts_tuition_2014 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,tuition_data_2014)

#2013

tuition_data_2013 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/tuition_data - 2013.csv")

Lib_arts_tuition_2013 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,tuition_data_2013)

#2012

tuition_data_2012 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/tuition_data - 2012.csv")

Lib_arts_tuition_2012 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,tuition_data_2012)

#2011

tuition_data_2011 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/tuition_data - 2011.csv")

Lib_arts_tuition_2011 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,tuition_data_2011)


#2010

tuition_data_2010 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/tuition_data - 2010.csv")

Lib_arts_tuition_2010 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,tuition_data_2010)


#2009

tuition_data_2009 <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/tuition_data - 2009.csv")

Lib_arts_tuition_2009 <-left_join(Top_50_Liberal_Arts_Colleges_2015_2018_College,tuition_data_2009)

write_csv(Lib_arts_tuition_2009, "Lib_arts_tuition_2009.csv")
write_csv(Lib_arts_tuition_2010, "Lib_arts_tuition_2010.csv")
write_csv(Lib_arts_tuition_2011, "Lib_arts_tuition_2011.csv")
write_csv(Lib_arts_tuition_2012, "Lib_arts_tuition_2012.csv")
write_csv(Lib_arts_tuition_2013, "Lib_arts_tuition_2013.csv")
write_csv(Lib_arts_tuition_2014, "Lib_arts_tuition_2014.csv")
write_csv(Lib_arts_tuition_2015, "Lib_arts_tuition_2015.csv")
write_csv(Lib_arts_tuition_2016, "Lib_arts_tuition_2016.csv")
write_csv(Lib_arts_tuition_2017, "Lib_arts_tuition_2017.csv")
write_csv(Lib_arts_tuition_2018, "Lib_arts_tuition_2018.csv")
write_csv(Lib_arts_tuition_2019, "Lib_arts_tuition_2019.csv")
write_csv(Lib_arts_tuition_2020, "Lib_arts_tuition_2020.csv")
write_csv(Lib_arts_tuition_2021, "Lib_arts_tuition_2021.csv")
write_csv(Lib_arts_tuition_2022, "Lib_arts_tuition_2022.csv")

```

$$Y_{it} = \alpha_i +\gamma_t + \sum\limits_{g}\sum\limits_{t \geq g} \delta_{it} T + x_{it} +\epsilon_{it}$$
$$yield \ rate = \frac{enrolled}{admitted}*100$$
$$log(\frac{\pi_{it}}{1+ \pi_{it}}) = \alpha_i +  \gamma_s + \beta_0 Endowment_{it} + \beta_0Peer\_divest\_prop $$
Where $\pi$ represents the probability that an institution will commit to divesting thier endowment from fossil fuels. 

Firstly, it is important to note some possible limitations, Specifically, it we have limited data on factors that incentivized a college to divest from fossil fuels. Much of this is related to and could be signaled by a number of things including students demographics, or college income/endowment

```{r}
library(did)
library(ggplot2)

# Load the data
data <- read.csv()

data$log_gdppc <- log(data$gdppc)

# Mapping for variable names to custom titles
yvar_titles <- list(
  "v2xeg_eqdr" = "Equal Distribution of Resources",
  "log_gdppc" = "GDP per capita"
)

gvar_titles <- list(
  "sy_govt_us_econgrowth" = "Government",
  "sy_faith_us_econgrowth" = "Religious",
  "sy_enterp_us_econgrowth" = "Private Enterprise"
)

# Function to perform DID analysis and plot event study with custom titles
perform_did_analysis <- function(yvar, gvar, filename_suffix) {
  result <- att_gt(yname = yvar,
                   tname = "year",
                   idname = "countryid",
                   gname = gvar,
                   control_group = "notyettreated",
                   data = data,
                   xformla = ~1)
 
  event_study <- aggte(result, type = "dynamic", na.rm = TRUE)
 
  x_limits <- c(-20, 20)
 
  # Plot the event study
  plot <- ggdid(event_study) +
    ggtitle(paste("Event Study -", gvar_titles[[gvar]], "on", yvar_titles[[yvar]])) +
    xlab("Time") +
    ylab("ATT Estimates") +
    theme_minimal(base_size = 15) +
    theme(
      plot.background = element_rect(fill = "white", color = NA),
      panel.background = element_rect(fill = "white", color = NA),
      panel.grid.major = element_line(color = "grey80"),
      panel.grid.minor = element_blank(),
      axis.text.x = element_text(angle = 90, hjust = 1, size = 8),
      axis.text.y = element_text(size = 10),
      plot.title = element_text(size = 14, hjust = 0.5) # Center the title
    ) +
    scale_x_continuous(limits = x_limits, breaks = seq(x_limits[1], x_limits[2], by = 1))
 
  # Adjust point and line sizes without changing colors
  plot$layers[[1]]$aes_params$size <- 3.5  # Points
  plot$layers[[2]]$aes_params$size <- 1.5  # Lines
 
  print(plot)
 
  ggsave(paste0("event_study_plot_", filename_suffix, ".png"), plot = plot, width = 12, height = 8, dpi = 300)
}

# Analysis and plots for 'govt', 'faith', 'enterp' using 'v2xeg_eqdr'
perform_did_analysis("v2xeg_eqdr", "sy_govt_us_econgrowth", "govt_v2xeg_eqdr")
perform_did_analysis("v2xeg_eqdr", "sy_faith_us_econgrowth", "faith_v2xeg_eqdr")
perform_did_analysis("v2xeg_eqdr", "sy_enterp_us_econgrowth", "enterp_v2xeg_eqdr")

# Analysis and plots for 'govt', 'faith', 'enterp' using 'log_gdppc'
perform_did_analysis("log_gdppc", "sy_govt_us_econgrowth", "govt_log_gdppc")
perform_did_analysis("log_gdppc", "sy_faith_us_econgrowth", "faith_log_gdppc")
perform_did_analysis("log_gdppc", "sy_enterp_us_econgrowth", "enterp_log_gdppc")
```



```{r}
College_panel_Divest_data_2<- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/College_panel - Divest_data (2).csv")

College_panel_College <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Downloads/College_panel - College.csv")

College_panel_Divest_data_3 <- left_join(College_panel_Divest_data_2,College_panel_College)

College_panel <- College_panel_Divest_data_3|>
  rename(divest_peers= `Divest _peers`)|>
  mutate(peer_prop = divest_peers/peer_num)

write_csv(College_panel, "College_panel.csv")

```

